Backbone-Store: An API for Automating Local Caching of Web Application Data

### 2012-05-21 paper/paper.tex
Added bibliography

\documentclass[12pt]{article}
\usepackage{fullpage}
\usepackage{setspace}
\usepackage{graphicx}

@@

There are several new client-side data storage options for web applications
with HTML5. Web SQL presents a database API similar to SQLite and provides
transactions. However, Web SQL is not supported by all of the major browsers,
with Firefox in particular refusing to ever support Web SQL. There are two
key-value storage options, called sessionStorage and localStorage, that have a
simple API (\verb=saveItem(key, value)=, \verb=getItem(key)=,
\verb=removeItem(key)=, and \verb=clear()=) for storing key-value pairs.
Session storage stores data only while a user is viewing a website, and
automatically clears the data when a user navigates away from the site. Local
storage persists data until it is deleted by the application or by the user
clearing all of the website's information from the browser. Local storage is
the best solution for cross-browser support and persistent storage.

Backbone-store, the project described in this paper, presents a new way for web
application programmers to easily save their web application's data on the
client to take advantage of the two benefits described above. This project is
an extension of the pure-Javascript Backbone.js library, which is used by many
companies to create web applications for browsers and mobile devices. Data
stored in Backbone.js applications are generally placed in either a Model
object or a Collection object, which is an ordered list of objects of one type
of Model. Backbone.js also provides View objects for managing the UI based on
the state of the Model or Collection objects.

@@

We created a simple server using Node.js for our test applications. Our timing
application presented a blank page which loaded a particular number of items
for each of the three types of models into collections from both localStorage
and from server requests. Three request URLs allowed the web application to use
Ajax to query the server for the data needed for each type of model. To easily
collect a large enough sample size of timing data, we had the server record
responses from the web application and print out batches of times for 15
requests to a CSV file. This allowed us to rapidly collect timing data for each
scenario.

@@

>>>>

\documentclass[12pt]{article}
\usepackage{fullpage}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{url}

@@

There are several new client-side data storage options for web applications
with HTML5. Web SQL \cite{websql} presents a database API similar to SQLite and provides
transactions. However, Web SQL is not supported by all of the major browsers,
with Firefox in particular refusing to ever support Web SQL. There are two
key-value storage options, called sessionStorage and localStorage \cite{localstorage}, that have a
simple API (\verb=saveItem(key, value)=, \verb=getItem(key)=,
\verb=removeItem(key)=, and \verb=clear()=) for storing key-value pairs.
Session storage stores data only while a user is viewing a website, and
automatically clears the data when a user navigates away from the site. Local
storage persists data until it is deleted by the application or by the user
clearing all of the website's information from the browser. Local storage is
the best solution for cross-browser support and persistent storage.

Backbone-store, the project described in this paper, presents a new way for web
application programmers to easily save their web application's data on the
client to take advantage of the two benefits described above. This project is
an extension of the pure-Javascript Backbone.js \cite{backbone} library, which is used by many
companies to create web applications for browsers and mobile devices. Data
stored in Backbone.js applications are generally placed in either a Model
object or a Collection object, which is an ordered list of objects of one type
of Model. Backbone.js also provides View objects for managing the UI based on
the state of the Model or Collection objects.

@@

We created a simple server using Node.js \cite{node} for our test applications. Our timing
application presented a blank page which loaded a particular number of items
for each of the three types of models into collections from both localStorage
and from server requests. Three request URLs allowed the web application to use
Ajax to query the server for the data needed for each type of model. To easily
collect a large enough sample size of timing data, we had the server record
responses from the web application and print out batches of times for 15
requests to a CSV file. This allowed us to rapidly collect timing data for each
scenario.

@@

\bibliographystyle{plain}
\bibliography{paper}
